Covariates analysis of UFL-Mayo-ISB RNASeq data of cerebellum tissue (realigned from synapse BAM with Picard-STAR-HTSeq)

### 2016-11-11 code/Rmd/Mayo_CBE_RNASeq_Realigned_SynBAM_StarHTSeq.Rmd
Minor changes

>>>>

### Comparison of reprocessed counts with source counts
```{r comp, fig.height=5, fig.width=5}
COUNT_OR = downloadFile('syn5201012')
rownames(COUNT_OR) = COUNT_OR$ensembl_id
COUNT_OR$ensembl_id = NULL

COUNT = COUNT %>%
  rownameToFirstColumn('GeneID') %>%
  dplyr::mutate(gene.id = GeneID) %>%
  tidyr::separate(GeneID, c('ensembl_gene_id','position'),sep = '\\.') %>%
  filter(ensembl_gene_id %in% rownames(COUNT_OR))
rownames(COUNT) = COUNT$ensembl_gene_id
COUNT = COUNT[intersect(rownames(COUNT), rownames(COUNT_OR)),intersect(colnames(COUNT), colnames(COUNT_OR))]
COUNT_OR = COUNT_OR[intersect(rownames(COUNT), rownames(COUNT_OR)),intersect(colnames(COUNT), colnames(COUNT_OR))]

cr = cor(COUNT, COUNT_OR, use = 'pairwise.complete.obs')
boxplot(diag(cr), main = 'Individual sample level correlation', ylab = 'Correlation', xlab = 'n=271')
```
